14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Fix benchmark selection for UC and MV tracks.

\header{Benchmark Selection.}
This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack,
modified to use named top-level assertions of the form \akey{(assert (! t
:named f ))}.
\todo{what if removing all benchmarks with one assertion doesn't leave enough benchmarks in a division?}

@@

\header{Benchmark Selection.}
This experimental track only has one division, QF\_BV. It will run on all
\emph{satisfiable} benchmarks from this division in the \maintrack.

@@

\header{Benchmark sources.}
Benchmarks for each division will be drawn from the SMT-LIB benchmark library.
The \maintrack will use a subset of all \emph{non-incremental} benchmarks and
the \inctrack will use a subset of all \emph{incremental} benchmarks. The
\challtrack will use all incremental and non-incremental benchmarks dedicated
to this track by their submitters. The \ucoretrack will use all unsatisfiable
\maintrack benchmarks, modified to use named top-level assertions.  The
\mvaltrack will use all satisfiable \maintrack benchmarks from the QF\_BV
division.

>>>>

\header{Benchmark Selection.}
This track will run on a selection of non-incremental benchmarks with status
\texttt{unsat} (as described on page~\pageref{benchmark-selection}), modified
to use named top-level assertions of the form \akey{(assert (! t :named f ))}.

@@

\header{Benchmark Selection.}
This experimental track only has one division, QF\_BV. It will run on all
selection of non-incremental benchmarks with status \texttt{sat} from logic
QF\_BV (as described on page~\pageref{benchmark-selection}).

@@

\header{Benchmark sources.}
Benchmarks for each division will be drawn from the SMT-LIB benchmark library.
The \maintrack will use a subset of all \emph{non-incremental} benchmarks and
the \inctrack will use a subset of all \emph{incremental} benchmarks. The
\challtrack will use all incremental and non-incremental benchmarks dedicated
to this track by their submitters. The \ucoretrack will use a selection of
non-incremental benchmarks with status \texttt{unsat} and more than one
top-level assertion, modified to use named top-level assertions.  The
\mvaltrack will use a selection of non-incremental benchmarks with status
\texttt{sat} from logic QF\_BV.
